FEM Model Analysis

### 2023-02-24 FEM_R/model_analysis_core.Rmd

```{r setup, include=FALSE}
# Need to set up the working directory
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/output/COMPLETE/"
knitr::opts_knit$set(root.dir = workingDir)

>>>>

```{r setup, include=FALSE}
# Need to set up the working directory
workingDir <- "/home/luke/Documents/WORK/E_FEM/E_FEM/output/COMPLETE/"
knitr::opts_knit$set(root.dir = workingDir)
